Equalizer Programming Guide

### 2008-05-15 Developer/ProgrammingGuide/paper.tex
Website: Update Equalizer presentation
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.3.2 for Equalizer 0.5+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Version for Equalizer 0.5\\
    1.3.1   & May 02, 2008 & Add statistics, improved images based on 1.2 print\\
    1.3.2   & May 05, 2008 & Add network distribution on eqPly model data\\
    1.3.3   & May 10, 2008 & File Format Appendix [incomplete]\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

\begin{center}
\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_SATTR\_HOSTNAME\\
  \textbf{Value} & string\\
  \textbf{Default} & ''localhost''\\
  \textbf{Description} & The hostname or IP address used to connect the
  server or node. When used for the server, the listening port of the
  server is bound to this address. When used for a node, the server
  first tries to connect to the render client node using this hostname,
  and then tries to launch the render client executable on this host.\\
  \hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_SATTR\_LAUNCH\_COMMAND\\
  \textbf{Value} & string\\
  \textbf{Default} & ssh -n \%h \%c \textgreater\& \%h.\%n.log [POSIX]\\
                   & ssh -n \%h \%c [WIN32]\\
  \textbf{Description} & The command used by the server to launch nodes
  which could not be connected. The launch command is executed from a
  process forked of the server process. The \% tokens are replaced by the
  server at runtime with concrete data: \%h is replaced by the hostname,
  \%c by the command to launch, including command line arguments and \%n
  by a node-unique identifier. Each command line argument are surrounded
  by launch command quotes.\\
  \hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_CATTR\_LAUNCH\_COMMAND\_QUOTE\\
  \textbf{Value} & character\\
  \textbf{Default} & ' [POSIX]\\
                   & '' [WIN32]\\
  \textbf{Description} & The server uses command line arguments to
  launch render client nodes correctly. This arguments might contain
  white spaces, and therefore have to be surrounded by quotes to
  identify their borders. Certain launch commands or shells use
  different conventions to separate command line arguments.\\
  \hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_IATTR\_TYPE\\
  \textbf{Value} & TCPIP \textbar \ SDP\\
  \textbf{Default} & TCPIP\\
  \textbf{Description} & The protocol for connections. SDP
  programmatically selects the socket direct protocol (AF\_INET\_SDP)
  provided by most InfiniBand protocol stacks.\\
  \hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_IATTR\_TCPIP\_PORT\\
  \textbf{Value} & unsigned\\
  \textbf{Default} & 0\\
  \textbf{Description} & The listening port used by the server or
  node. For nodes, the port can be used to contact pre-started, resident
  render client nodes or to use a specific port for the node. If 0 is
  specified, a random port is chosen. Note that a server with no
  connections automatically creates a default connection using the
  server's default port.\\
  \hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_CONNECTION\_IATTR\_LAUNCH\_TIMEOUT\\
\textbf{Value} & unsigned\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_CONFIG\_FATTR\_EYE\_BASE\\
\textbf{Value} & float\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_PIPE\_IATTR\_HINT\_THREAD\\
\textbf{Value} & OFF \textbar \ ON\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_STEREO\\
\textbf{Value} & OFF \textbar \ ON \textbar \ AUTO\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_DOUBLEBUFFER\\
\textbf{Value} & OFF \textbar \ ON \textbar \ AUTO\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_DECORATION\\
\textbf{Value} & OFF \textbar \ ON\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_FULLSCREEN\\
\textbf{Value} & OFF \textbar \ ON\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_SWAPSYNC\\
\textbf{Value} & OFF \textbar \ ON // AGL, WGL only\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_DRAWABLE\\
\textbf{Value} & window \textbar \ pbuffer\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_STATISTICS\\
\textbf{Value} & off \textbar \ fastest [on] \textbar \ nicest\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_PLANES\_COLOR\\
\textbf{Value} & unsigned\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_PLANES\_ALPHA\\
\textbf{Value} & unsigned\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_PLANES\_DEPTH\\
\textbf{Value} & unsigned\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_PLANES\_STENCIL\\
\textbf{Value} & unsigned\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_CHANNEL\_IATTR\_HINT\_STATISTICS\\
\textbf{Value} & OFF \textbar \ FASTEST [ ON ] \textbar \ NICEST\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_MODE\\
\textbf{Value} & QUAD \textbar \ ANAGLYPH\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_ANAGLYPH\_LEFT\_MASK\\
\textbf{Value} & [ RED GREEN BLUE ]\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_ANAGLYPH\_RIGHT\_MASK\\
\textbf{Value} & [ RED GREEN BLUE ]\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_COMPOUND\_IATTR\_UPDATE\_FOV\\
\textbf{Value} & HORIZONTAL [ON] \textbar \ VERTICAL \textbar \ OFF\\
\textbf{Default} & \\
\textbf{Description} & \\
\hline
\end{tabularx}\\[\smallskipamount]
\end{center}

>>>>

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.3.3 for Equalizer 0.5+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Version for Equalizer 0.5\\
    1.3.1   & May 02, 2008 & Add statistics, improved images based on 1.2 print\\
    1.3.2   & May 05, 2008 & Add network distribution on eqPly model data\\
    1.3.3   & May 10-13, 2008 & File Format Appendix [incomplete]\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

\begin{center}
\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_SATTR\_HOSTNAME\\
  \textbf{Value} & string\\
  \textbf{Default} & ''localhost''\\
  \textbf{Details} & The hostname or IP address used to connect the
  server or node. When used for the server, the listening port of the
  server is bound to this address. When used for a node, the server
  first tries to connect to the render client node using this hostname,
  and then tries to launch the render client executable on this host.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_SATTR\_LAUNCH\_COMMAND\\
  \textbf{Value} & string\\
  \textbf{Default} & ssh -n \%h \%c \textgreater\& \%h.\%n.log [POSIX]\\
                   & ssh -n \%h \%c [WIN32]\\
  \textbf{Details} & The command used by the server to launch nodes
  which could not be connected. The launch command is executed from a
  process forked of the server process. The \% tokens are replaced by the
  server at runtime with concrete data: \%h is replaced by the hostname,
  \%c by the command to launch, including command line arguments and \%n
  by a node-unique identifier. Each command line argument are surrounded
  by launch command quotes.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_CATTR\_LAUNCH\_COMMAND\_QUOTE\\
  \textbf{Value} & character\\
  \textbf{Default} & ' [POSIX]\\
                   & '' [WIN32]\\
  \textbf{Details} & The server uses command line arguments to
  launch render client nodes correctly. This arguments might contain
  white spaces, and therefore have to be surrounded by quotes to
  identify their borders. Certain launch commands or shells use
  different conventions to separate command line arguments.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_IATTR\_TYPE\\
  \textbf{Value} & TCPIP \textbar \ SDP\\
  \textbf{Default} & TCPIP\\
  \textbf{Details} & The protocol for connections. SDP
  programmatically selects the socket direct protocol (AF\_INET\_SDP)
  provided by most InfiniBand protocol stacks.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_IATTR\_TCPIP\_PORT\\
  \textbf{Value} & unsigned\\
  \textbf{Default} & 0\\
  \textbf{Details} & The listening port used by the server or
  node. For nodes, the port can be used to contact pre-started, resident
  render client nodes or to use a specific port for the node. If 0 is
  specified, a random port is chosen. Note that a server with no
  connections automatically creates a default connection using the
  server's default port.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONNECTION\_IATTR\_LAUNCH\_TIMEOUT\\
  \textbf{Value} & unsigned\\
  \textbf{Default} & 60'000\\
  \textbf{Details} & Defines the timeout in milliseconds to wait for
  an auto-launched node. If the render client process did not contact
  the server within that time, the node is considered to be unreachable
  and the initialization of the configuration fails.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_CONFIG\_FATTR\_EYE\_BASE\\
  \textbf{Value} & float\\
  \textbf{Default} & 0.05\\
  \textbf{Details} & The distance in meters between the left and the
  right eye, i.e., the eye separation. The eye base influences the
  frustum during stereo rendering. See \sref{sTracking} for details.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_PIPE\_IATTR\_HINT\_THREAD\\
  \textbf{Value} & OFF \textbar \ ON\\
  \textbf{Default} & ON\\
  \textbf{Details} & Determines if all task methods for a pipe and its
  children are executed from a separate operating system thread
  (default) or from the node main thread. Non-threaded pipes have
  certain performance
  limitations and should only be used if really necessary.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_STEREO\\
  \textbf{Value} & OFF \textbar \ ON \textbar \ AUTO\\
  \textbf{Default} & AUTO\\
  \textbf{Details} & Determines if the window selects a quad-buffered
  stereo visual. When set to AUTO, the window initialization methods try
  to allocate a stereo visual, but fall back to a mono visual if
  allocation fails.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_DOUBLEBUFFER\\
  \textbf{Value} & OFF \textbar \ ON \textbar \ AUTO\\
  \textbf{Default} & AUTO\\
  \textbf{Details} & Determines if the window selects a double-buffered
  stereo visual. When set to AUTO, the window initialization methods try
  to allocate a double-buffered visual, but fall back to a
  single-buffered visual if allocation fails.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_DECORATION\\
  \textbf{Value} & OFF \textbar \ ON\\
  \textbf{Default} & ON\\
  \textbf{Details} & When set to OFF, window borders and other
  decorations are disabled, and typically the window can not be moved or
  resized. This option is useful for source windows during
  decomposition. The implementation is window-system specific.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_FULLSCREEN\\
  \textbf{Value} & OFF \textbar \ ON\\
  \textbf{Default} & OFF\\
  \textbf{Details} & When set to ON, the window displays in
  fullscreen. This option forces window decorations to be OFF. The
  implementation is window-system specific.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_SWAPSYNC\\
  \textbf{Value} & OFF \textbar \ ON\\
  \textbf{Default} & ON\\
  \textbf{Details} & Determines if the buffer swap is synchronized with
  the vertical retrace of the display. This option is currently not
  implemented for GLX. For WGL, the WGL\_EXT\_swap\_control extension is
  required. For optimal performance, set swap synchronization to OFF for
  source-only windows.\\
  \hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_DRAWABLE\\
\textbf{Value} & window \textbar \ pbuffer\\
\textbf{Default} & window\\
\textbf{Details} & Selects the window's drawable type.\\
\hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_STATISTICS\\
\textbf{Value} & off \textbar \ fastest [on] \textbar \ nicest\\
\textbf{Default} & \\
\textbf{Details} & \\
\hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_PLANES\_COLOR\\
\textbf{Value} & unsigned\\
\textbf{Default} & \\
\textbf{Details} & \\
\hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_PLANES\_ALPHA\\
\textbf{Value} & unsigned\\
\textbf{Default} & \\
\textbf{Details} & \\
\hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_PLANES\_DEPTH\\
\textbf{Value} & unsigned\\
\textbf{Default} & \\
\textbf{Details} & \\
\hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_WINDOW\_IATTR\_PLANES\_STENCIL\\
\textbf{Value} & unsigned\\
\textbf{Default} & \\
\textbf{Details} & \\
\hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_CHANNEL\_IATTR\_HINT\_STATISTICS\\
\textbf{Value} & OFF \textbar \ FASTEST [ ON ] \textbar \ NICEST\\
\textbf{Default} & \\
\textbf{Details} & \\
\hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_MODE\\
\textbf{Value} & QUAD \textbar \ ANAGLYPH\\
\textbf{Default} & \\
\textbf{Details} & \\
\hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_ANAGLYPH\_LEFT\_MASK\\
\textbf{Value} & [ RED GREEN BLUE ]\\
\textbf{Default} & \\
\textbf{Details} & \\
\hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_ANAGLYPH\_RIGHT\_MASK\\
\textbf{Value} & [ RED GREEN BLUE ]\\
\textbf{Default} & \\
\textbf{Details} & \\
\hline
\end{tabularx}\\\vfill

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Name} & EQ\_COMPOUND\_IATTR\_UPDATE\_FOV\\
\textbf{Value} & HORIZONTAL [ON] \textbar \ VERTICAL \textbar \ OFF\\
\textbf{Default} & \\
\textbf{Details} & \\
\hline
\end{tabularx}\\
\end{center}
